---
title: "P8105_hw4_hc3212"
author: "Hening cui"
date: "2021/10/14"
output: github_document
---

## Homework 3

```{r set, echo = FALSE, message = FALSE}
library(tidyverse)
library(p8105.datasets)
library(dplyr)
library(ggplot2)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)
options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

__Load and describe instacart data set.__

```{r load_data}
data("instacart")
```

The instacart data set contains `r nrow(instacart)` observations and `r ncol(instacart)` variables. The data set is in a "long" format.The variable contains `r ls(instacart)`. Every user has an unique user id, and each order has an unique order id. Every product was assigned a product id, the aisle together with aisle id showed the category of product. Product belongs to different department and could distinguished by department id. Reorder indicated whether the product has been ordered before, with 1 means yes, 0 means no. Order dow and order hour of day means at which hour in the weekday it was ordered. Take row one as an example.

```{r, echo = FALSE}
head(instacart, num = 3) %>% 
  knitr::kable()
```


Row one means in order 1, user 112108 add 4 boxes of Bulgarian yogurt first in to the cart. This product was also ordered 10 days before. Bulgarian yogurt was identified as 49302 and belongs to yogurt category (id 120) in dairy eggs department (id 16). The order was at 10 o'clock in Thursday.

__How many aisles are there, and which aisles are the most items ordered from?__
```{r aisle_count}
instacart %>% 
  pull(aisle_id) %>% 
  n_distinct()

instacart %>% 
  group_by(aisle_id, aisle) %>% 
  summarize(n_item = n()) %>% 
  arrange(desc(n_item))
```

There totally 134 aisles, fresh_vegetables(id:83) had most items ordered from.

__Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.__

```{r aisle_plot, message = FALSE}
instacart %>% 
  group_by(aisle_id, aisle) %>% 
  summarize(n_item = n()) %>% 
  filter(n_item > 10000) %>% 
  arrange(desc(n_item)) %>% 
  ggplot() +
  geom_bar(aes(x = n_item, y = aisle, fill = aisle),stat = 'identity', alpha = 0.5) +
  labs(
    title = "No. of items vs Aisle",
    y = "Aisle", 
    x = "No. of item",
  ) +
  scale_x_continuous( 
    breaks = c(10000, 20000, 40000, 80000, 120000)
    ) +
  theme(
    legend.position = 'none',
    axis.text.y = element_text(size = 6),
    axis.text.x = element_text(size = 5))
```

__Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.__

```{r popular3, message = FALSE}
backing = 
  instacart %>% 
  filter(aisle == "baking ingredients") %>% 
  group_by(aisle, product_name) %>% 
  summarize(n_item = n()) %>% 
  arrange(desc(n_item)) %>% 
  head(3)

dog = 
  instacart %>% 
  filter(aisle == c("dog food care")) %>% 
  group_by(aisle, product_name) %>% 
  summarize(n_item = n()) %>% 
  arrange(desc(n_item)) %>% 
  head(3)  

vegetable = 
  instacart %>% 
  filter(aisle == "packaged vegetables fruits") %>% 
  group_by(aisle, product_name) %>% 
  summarize(n_item = n()) %>% 
  arrange(desc(n_item)) %>% 
  head(3)   

bind_rows(backing, dog, vegetable) %>% 
  knitr::kable()
```

__Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).__

```{r meantime}
instacart %>% 
  filter(product_name == c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  select(order_dow, order_hour_of_day, product_name) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(meant = mean(order_hour_of_day)) %>% 
  mutate(
    order_dow = case_when(
      order_dow == 1 ~ "Monday",
      order_dow == 2 ~ "Tuesday",
      order_dow == 3 ~ "Wednesday",
      order_dow == 4 ~ "Thursday",
      order_dow == 5 ~ "Friday",
      order_dow == 6 ~ "Saturday",
      order_dow == 0 ~ "Sunday",
    )
  ) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = meant
  ) %>% 
  knitr::kable()
```






































